Notes on the low density parameters in {\tt MAESTRO}

### 2009-06-08 docs/lo_density/lo_density.tex
more marginpars

\item In {\tt init\_base\_state}, we give a warning of {\tt base\_cutoff\_density}
  is smaller than the minimum model density.  Then, if {\tt anelastic\_cutoff} 
  $<$ {\tt base\_cutoff\_density} we abort the program.

@@

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0 > {\tt base\_cutoff\_density}$ (in spherical).
  \MarginPar{Revisit this.}

@@

\item In {\tt update\_scal}, if the new $\rho$ is less than 
  {\tt base\_cutoff\_density} and {\tt do\_eos\_h\_above\_cutoff},  
  we call the EOS to compute $h$.

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.

>>>>

\item In {\tt init\_base\_state}, we give a warning of {\tt base\_cutoff\_density}
  is smaller than the minimum model density.  Then, if ${\tt anelastic\_cutoff} 
  < {\tt base\_cutoff\_density}$ we abort the program.

@@

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0^{\rm cart} > {\tt base\_cutoff\_density}$ 
  (in spherical).
  \MarginPar{Spherical should cue off the coordinate.}

@@

\item In {\tt update\_scal}, if $\rho < {\tt base\_cutoff\_density}$
   and {\tt do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.
  \MarginPar{Perhaps $\rho \le {\tt base\_cutoff\_density}$}

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.
  \MarginPar{Cue off the coordinate?}
